RunTime-Assisted Convergence \\ in Replicated Data Types

### 2022-04-25 proofs.tex
Move appendix (proofs) to separate document
Build it with:

latexmk -pdf appendix

% \begin{theorem}[{\bf Uniqueness of LCA}]
%   Assuming that we start with the initial state $\Delta_{\odot}$, the
%   transition rules in Fig.~\ref{fig:sem-head-pull} will always lead to
%   a state $\Delta = ((V,E),B,H,L)$ where every distinct pair of
%   branches, $b_1 \in dom(H)$ and $b_2 \in dom (H)$, has a single LCA given by
%   $L(b_1,b_2)$, which is equal to $L(b_2,b_1)$.
% \end{theorem}
\begin{proof}[Proof of Lemma~\ref{lem:lca-uniqueness}]

@@

    \item Case {\sc Merge}: The proof follows from the premise
    of \rulelabel{Merge}, which requires that, for every branch $b''$ in
    the system, the LCA of $b''$ with merging branches $b$ and $b'$ be
    causally related, i.e, $L(b,b'') \reaches L(b',b'') ~\disj$
    $L(b',b'') \reaches L(b,b'')$. Fig.~\ref{fig:merge-precondition}
    helps visualize this condition in the most general case when
    (\rom{1}). Branches $b$, $b'$, and $b''$ are distinct, and
    (\rom{2}). Their LCAs $L(b,b'')$ and $L(b',b'')$ lie on a distinct
    pair of branches not equal to $b$, $b'$, and $b''$. In the figure,
    once you merge $b'$ into $b$, every version $v$ that is an
    ancestor of $L(b',b'')$, i.e., $v \reaches L(b',b'')$, will be  a
    common ancestor of $H(b)$ and $H(b'')$. Clearly, $L(b',b'')$ is
    the lowest among such common ancestors. But the current lowest
    common ancestor of $b$ and $b''$ is $L(b,b'')$. This leads to
    the condition where there are two lowest common ancestors --
    $L(b',b'')$ and $L(b,b'')$, \emph{unless} both are ancestrally
    related. The premise
    $L(b,b'') \reaches L(b',b'') \disj L(b',b'') \reaches L(b,b'')$
    guarantees that they are causally-related, ensuring the uniqueness
    of LCA.

@@

% \begin{lemma}[Commit sets grow monotonically]
%   \label{lem:commit-monotonicity}
%   Let $\Delta = ((V,E),N,C,H,L)$ be the state of a version-control
%   system. Forall $v_1,v_2 \in V$, if $v_1 \reaches v_2$ then $C(v_1)
%   \subseteq C(v_2)$.
% \end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:commit-monotonicity}]
  Straightforward induction on $\Delta$.
\end{proof}

@@

\begin{proof}[Proof of Lemma~\ref{lem:commit-disjointness}]

@@

              Lemma~\ref{lem:commit-monotonicity} we know:

@@

            \item Case $L(b',b'') \reaches L(b,b'')$: From
              Lemma~\ref{lem:commit-monotonicity} we know:
              \begin{smathpar}
              \begin{array}{lr}
                C(L(b',b'')) \subseteq C(L(b,b'')) & H5\\
              \end{array}
              \end{smathpar}
              The Goal is to prove the following:
              \begin{smathpar}
              \begin{array}{c}
                C'(v) - C'(L'(b,b'')) ~\cap~ C'(v'') - C'(L'(b,b''))
                ~=~ \emptyset\\
              \end{array}
              \end{smathpar}
              We shall now rewrite the goal through a series of
              equalities. First, since $C'(v) = C(v_{old}) \cup
              C(v')$, and $L'(b,b'') = L(b,b'')$ (since $L(b',b'')
              \reaches L(b,b'')$ as per our assumption in this case),
              and $C'(v'') = C(v'')$:
              \begin{smathpar}
              \begin{array}{c}
                (C(v_{old}) \cup C(v')) - C(L(b,b'')) \\
                ~~\cap~ C(v'') - C(L(b,b''))
                ~=~ \emptyset\\
              \end{array}
              \end{smathpar}
              Rewrite using Algebraic Law 3:
              \begin{smathpar}
              \begin{array}{c}
                (C(v_{old}) - C(L(b,b'')) ~\cup~ C(v') - C(L(b,b'')))\\
                ~~\cap~ C(v'') - C(L(b,b'')) ~=~ \emptyset\\
              \end{array}
              \end{smathpar}
              Rewrite using Algebraic Law 4:
              \begin{smathpar}
              \begin{array}{c}
                C(v_{old}) - C(L(b,b'')) ~\cap~ C(v'') -
                C(L(b,b'')) \\
                \hspace*{0.1in}
                \cup~~ C(v') - C(L(b,b'')) ~\cap~ C(v'') - C(L(b,b''))
                ~~=~~ \emptyset\\
              \end{array}
              \end{smathpar}
              Rewrite using IH1:
              \begin{smathpar}
              \begin{array}{c}
                C(v') - C(L(b,b'')) ~\cap~ C(v'') -
                C(L(b,b'')) ~=~ \emptyset\\
              \end{array}
              \end{smathpar}
              Apply Algebraic Law2 with $C := L(b',b'')$:
              \begin{smathpar}
              \begin{array}{c}
                C(v') - C(L(b',b'')) ~\cap~ C(v'') - C(L(b',b''))
                ~=~ \emptyset \\
                ~~\conj~ L(b',b'') \subseteq L(b,b'')\\
              \end{array}
              \end{smathpar}
              Now both conjuncts of the goal follow from hypotheses
              $IH2$ and $H5$, respectively.
          \end{itemize}
      \end{itemize}

@@

% \begin{theorem}[{\bf Convergence}]
%   Let $\Delta = ((V,E),N,C,H,L)$ be the state of a version-control
%   system. Forall distinct $b_1, b_2 \in dom(H)$, and $v_1, v_2 \in V$ s.t.
%   $v_1 = H(b_1)$ and $v_2 = H(b_2)$, the following is true:
%   $C(v_1) = C(v_2) \Rightarrow N(v_1) = N(v_2)$.
% \end{theorem}
\begin{proof}[Proof of Theorem~\ref{thm:convergence}]
  Proof by induction on $\Delta$. Base case trivially satisfies as
  there are no two branches in $\Delta_{\odot}$. Inductive proof has
  four cases corresponding to the four rules in
  Fig.~\ref{fig:git-semantics}:
  \begin{itemize}
    \item Case {\sc Commit}: Branch $b$ is extended with a fresh
      commit $c$, hence there does not exist another branch whose head
      has same commit set as $H'(b)$.

@@

    \item Case {\sc Merge}:  In all the cases where $b_1 \neq b$ and
      $b_2 \neq b$, proof follows from IH because nothing changes for
      these branches in $\Delta'$. We shall therefore focus on the
      case when one of $b_1$ or $b_2$ is $b$. Without loss of
      generality, let's assume $b_1 = b$. Two cases now depending on
      what $b_2$ is:
      \begin{itemize}
        \item Case $b_2 = b'$: The relevant premise of {\sc Merge} is
          reproduced below:
          \begin{smathpar}
          \begin{array}{lr}
            C(H(b)) \supset C(L(b,b')) & H0\\
          \end{array}
          \end{smathpar}
          We shall prove that $C'(H'(b_1))$ cannot be equal to
          $C'(H'(b_2))$ by first assuming that they are equal and then
          deriving a contradiction.
          \begin{smathpar}
          \begin{array}{lr}
            C'(H'(b_1)) = C'(H'(b_2)) & H1\\
          \end{array}
          \end{smathpar}
          Since $b_1 = b$, and $b_2 = b'$, and $C'(H'(b')) = C(H(b'))$:
          \begin{smathpar}
          \begin{array}{lr}
            C'(H'(b)) = C(H(b')) & \\
          \end{array}
          \end{smathpar}
          Since $C'(H'(b')) = C(H(b)) \cup C(H(b'))$:
          \begin{smathpar}
          \begin{array}{lr}
            C(H(b)) \cup C(H(b'))= C(H(b')) & H2\\
          \end{array}
          \end{smathpar}
          From Lemma~\ref{lem:commit-disjointness} on $\Delta$, we
          know the following:
          \begin{smathpar}
          \begin{array}{lr}
            C(H(b)) - C(L(b,b'))\\
            \hspace*{0.5in}~\cap~ C(H(b')) - C(L(b,b')) ~=~
            \emptyset & H3\\
          \end{array}
          \end{smathpar}
          Rewriting H3 using H2:
          \begin{smathpar}
          \begin{array}{lr}
            C(H(b)) - C(L(b,b'))\\
            \hspace*{0.25in}\cap~~ (C(H(b)) \cup C(H(b')) - C(L(b,b')) ~=~
            \emptyset & \\
          \end{array}
          \end{smathpar}
          Rewriting using Algebraic Law3:
          \begin{smathpar}
          \begin{array}{lr}
            C(H(b)) - C(L(b,b')) ~~\cap\\
            (C(H(b)) - C(L(b,b')) ~\cup~ C(H(b')) - C(L(b,b'))) ~=~ \emptyset & \\
          \end{array}
          \end{smathpar}
          Rewriting using Algebraic Law4:
          \begin{smathpar}
          \begin{array}{lr}
            (C(H(b)) - C(L(b,b')) ~\cap~ C(H(b)) - C(L(b,b')))\\
            ~~\cup~~ (C(H(b)) - C(L(b,b')) ~\cap~ C(H(b')) - C(L(b,b'))) 
            ~=~ \emptyset & \\
          \end{array}
          \end{smathpar}
          Simplifying, and Rewriting using $H3$:
          \begin{smathpar}
          \begin{array}{lr}
            C(H(b)) - C(L(b,b')) ~=~ \emptyset & \\
          \end{array}
          \end{smathpar}
          Which is possible if and only if:
          \begin{smathpar}
          \begin{array}{lr}
            C(H(b)) \subseteq C(L(b,b')) & H4\\
          \end{array}
          \end{smathpar}
          $H0$ and $H4$ now result in a contradiction.

        \item Case $b_2 = b'' \neq b'$: Premises of {\sc Merge}:
          \begin{smathpar}
          \begin{array}{lr}
            C(H(b)) \supset C(L(b,b'))& H1\\
            C(H(b')) \supset C(L(b,b'))& H2\\
            L(b,b'') \reaches L(b',b'') \disj L(b',b'') \reaches
            L(b,b'') & H3\\
          \end{array}
          \end{smathpar}
          From the conclusion of {\sc Merge}:
          \begin{smathpar}
          \begin{array}{lr}
            C'(H'(b)) = C(H(b)) \cup C(H(b')) & H4\\
            C'(H'(b'')) = C(H(b'')) & H5\\
          \end{array}
          \end{smathpar}
          And the premise of the theorem:
          \begin{smathpar}
          \begin{array}{lr}
            C'(H'(b)) = C'(H'(b'')) & \\
          \end{array}
          \end{smathpar}
          Due to $H5$, this is equivalent to:
          \begin{smathpar}
          \begin{array}{lr}
            C'(H'(b)) = C(H(b'')) & H6\\
          \end{array}
          \end{smathpar}
          From Lemma~\ref{lem:commit-disjointness} on $H'(b')$ and
          $H'(b'') = H(b'')$:
          \begin{smathpar}
          \begin{array}{lr}
            C'(H'(b)) - C'(L'(b,b'')) ~\cap\\
            \hspace*{0.5in}C(H(b'')) - C'(L'(b,b''))
            ~=~ \emptyset & \\
          \end{array}
          \end{smathpar}
          Rewriting using $H6$:
          \begin{smathpar}
          \begin{array}{lr}
            C'(H'(b)) - C'(L'(b,b'')) ~=~ \emptyset & \\
          \end{array}
          \end{smathpar}
          Hence:
          \begin{smathpar}
          \begin{array}{lr}
            C'(H'(b)) \subseteq C'(L'(b,b''))
          \end{array}
          \end{smathpar}
          Rewriting using $H4$:
          \begin{smathpar}
          \begin{array}{lr}
            C(H(b)) \cup C(H(b')) ~\subseteq~ C'(L'(b,b'')) & H7\\
          \end{array}
          \end{smathpar}
          Let us distruct $H3$ and consider the two disjuncts
          separately:
          \begin{itemize}
            \item Case $L(b,b'') \reaches L(b',b'')$: From the
              conclusion of {\sc Merge}:
              \begin{smathpar}
              \begin{array}{lr}
                L'(b,b'') = L(b',b'') & H8\\
              \end{array}
              \end{smathpar}
              Rewriting $H7$ using $H8$:
              \begin{smathpar}
              \begin{array}{lr}
                C(H(b)) \cup C(H(b')) ~\subseteq~ C(L(b',b'')) & H7\\
              \end{array}
              \end{smathpar}
              Which tells us:
              \begin{smathpar}
              \begin{array}{lr}
                C(H(b)) \subseteq C(L(b',b'')) & H9 \\
              \end{array}
              \end{smathpar}
              Note that $L(b',b'')$ is LCA of $H(b')$ and $H(b'')$,
              hence $L(b',b'') \reaches H(b')$. From
              Lemma~\ref{lem:commit-monotonicity}, we get:
              \begin{smathpar}
              \begin{array}{lr}
                C(L(b',b'')) \subseteq C(H(b')) & H10\\
              \end{array}
              \end{smathpar}
              From $H9$ and $H10$:
              \begin{smathpar}
              \begin{array}{lr}
                C(H(b)) \subseteq C(H(b')) &  H11\\
              \end{array}
              \end{smathpar}
              Lemma~\ref{lem:commit-disjointness} on $H(b)$ and
              $H(b')$ tells us:
              \begin{smathpar}
              \begin{array}{lr}
                C(H(b)) - C(L(b,b')) ~\cap\\
                \hspace*{0.5in}C(H(b')) - C(L(b,b')) ~=~
                \emptyset & H12\\
              \end{array}
              \end{smathpar}
              Applying Algebraic Law 5 on $H11$ and $H12$:
              \begin{smathpar}
              \begin{array}{lr}
                C(H(b)) \subseteq C(L(b,b'))
              \end{array}
              \end{smathpar}
              Which contradicts $H1$. Hence $C'(H'(b))$ cannot be
              equal to $C'(H'(b''))$.

>>>>

% \begin{theorem}[{\bf Uniqueness of LCA}]
%   Assuming that we start with the initial state $\Delta_{\odot}$, the
%   transition rules in Fig.~\ref{fig:sem-head-pull} will always lead to
%   a state $\Delta = ((V,E),B,H,L)$ where every distinct pair of
%   branches, $b_1 \in dom(H)$ and $b_2 \in dom (H)$, has a single LCA given by
%   $L(b_1,b_2)$, which is equal to $L(b_2,b_1)$.
% \end{theorem}
\begin{proof}[Proof of Lemma~3.4]

@@

    \item Case {\sc Merge}: The proof follows from the premise
    of \rulelabel{Merge}, which requires that, for every branch $b''$ in
    the system, the LCA of $b''$ with merging branches $b$ and $b'$ be
    causally related, i.e, $L(b,b'') \reaches L(b',b'') ~\disj$
    $L(b',b'') \reaches L(b,b'')$. Fig.~7
    helps visualize this condition in the most general case when
    (\rom{1}). Branches $b$, $b'$, and $b''$ are distinct, and
    (\rom{2}). Their LCAs $L(b,b'')$ and $L(b',b'')$ lie on a distinct
    pair of branches not equal to $b$, $b'$, and $b''$. In the figure,
    once you merge $b'$ into $b$, every version $v$ that is an
    ancestor of $L(b',b'')$, i.e., $v \reaches L(b',b'')$, will be  a
    common ancestor of $H(b)$ and $H(b'')$. Clearly, $L(b',b'')$ is
    the lowest among such common ancestors. But the current lowest
    common ancestor of $b$ and $b''$ is $L(b,b'')$. This leads to
    the condition where there are two lowest common ancestors --
    $L(b',b'')$ and $L(b,b'')$, \emph{unless} both are ancestrally
    related. The premise
    $L(b,b'') \reaches L(b',b'') \disj L(b',b'') \reaches L(b,b'')$
    guarantees that they are causally-related, ensuring the uniqueness
    of LCA.

@@

% \begin{lemma}[Commit sets grow monotonically]
%   \label{lem:commit-monotonicity}
%   Let $\Delta = ((V,E),N,C,H,L)$ be the state of a version-control
%   system. Forall $v_1,v_2 \in V$, if $v_1 \reaches v_2$ then $C(v_1)
%   \subseteq C(v_2)$.
% \end{lemma}
\begin{proof}[Proof of Lemma~3.5]
  Straightforward induction on $\Delta$.
\end{proof}

@@

\begin{proof}[Proof of Cor.~3.6]

@@

              Lemma~3.5 we know:

@@

            \item Case $L(b',b'') \reaches L(b,b'')$: From
              Lemma~3.5 we know:
              \begin{smathpar}
              \begin{array}{lr}
                C(L(b',b'')) \subseteq C(L(b,b'')) & H5\\
              \end{array}
              \end{smathpar}
              The Goal is to prove the following:
              \begin{smathpar}
              \begin{array}{c}
                C'(v) - C'(L'(b,b'')) ~\cap~ C'(v'') - C'(L'(b,b''))
                ~=~ \emptyset\\
              \end{array}
              \end{smathpar}
              We shall now rewrite the goal through a series of
              equalities. First, since $C'(v) = C(v_{old}) \cup
              C(v')$, and $L'(b,b'') = L(b,b'')$ (since $L(b',b'')
              \reaches L(b,b'')$ as per our assumption in this case),
              and $C'(v'') = C(v'')$:
              \begin{smathpar}
              \begin{array}{c}
                (C(v_{old}) \cup C(v')) - C(L(b,b'')) \\
                ~~\cap~ C(v'') - C(L(b,b''))
                ~=~ \emptyset\\
              \end{array}
              \end{smathpar}
              Rewrite using Algebraic Law 3:
              \begin{smathpar}
              \begin{array}{c}
                (C(v_{old}) - C(L(b,b'')) ~\cup~ C(v') - C(L(b,b'')))\\
                ~~\cap~ C(v'') - C(L(b,b'')) ~=~ \emptyset\\
              \end{array}
              \end{smathpar}
              Rewrite using Algebraic Law 4:
              \begin{smathpar}
              \begin{array}{c}
                C(v_{old}) - C(L(b,b'')) ~\cap~ C(v'') -
                C(L(b,b'')) \\
                \hspace*{0.1in}
                \cup~~ C(v') - C(L(b,b'')) ~\cap~ C(v'') - C(L(b,b''))
                ~~=~~ \emptyset\\
              \end{array}
              \end{smathpar}
              Rewrite using IH1:
              \begin{smathpar}
              \begin{array}{c}
                C(v') - C(L(b,b'')) ~\cap~ C(v'') -
                C(L(b,b'')) ~=~ \emptyset\\
              \end{array}
              \end{smathpar}
              Apply Algebraic Law2 with $C := L(b',b'')$:
              \begin{smathpar}
              \begin{array}{c}
                C(v') - C(L(b',b'')) ~\cap~ C(v'') - C(L(b',b''))
                ~=~ \emptyset \\
                ~~\conj~ L(b',b'') \subseteq L(b,b'')\\
              \end{array}
              \end{smathpar}
              Now both conjuncts of the goal follow from hypotheses
              $IH2$ and $H5$, respectively.
          \end{itemize}
      \end{itemize}

@@

% \begin{theorem}[{\bf Convergence}]
%   Let $\Delta = ((V,E),N,C,H,L)$ be the state of a version-control
%   system. Forall distinct $b_1, b_2 \in dom(H)$, and $v_1, v_2 \in V$ s.t.
%   $v_1 = H(b_1)$ and $v_2 = H(b_2)$, the following is true:
%   $C(v_1) = C(v_2) \Rightarrow N(v_1) = N(v_2)$.
% \end{theorem}
\begin{proof}[Proof of Theorem~3.7]
  Proof by induction on $\Delta$. Base case trivially satisfies as
  there are no two branches in $\Delta_{\odot}$. Inductive proof has
  four cases corresponding to the four rules in
  Fig.~6:
  \begin{itemize}
    \item Case {\sc Commit}: Branch $b$ is extended with a fresh
      commit $c$, hence there does not exist another branch whose head
      has same commit set as $H'(b)$.

@@

    \item Case {\sc Merge}:  In all the cases where $b_1 \neq b$ and
      $b_2 \neq b$, proof follows from IH because nothing changes for
      these branches in $\Delta'$. We shall therefore focus on the
      case when one of $b_1$ or $b_2$ is $b$. Without loss of
      generality, let's assume $b_1 = b$. Two cases now depending on
      what $b_2$ is:
      \begin{itemize}
        \item Case $b_2 = b'$: The relevant premise of {\sc Merge} is
          reproduced below:
          \begin{smathpar}
          \begin{array}{lr}
            C(H(b)) \supset C(L(b,b')) & H0\\
          \end{array}
          \end{smathpar}
          We shall prove that $C'(H'(b_1))$ cannot be equal to
          $C'(H'(b_2))$ by first assuming that they are equal and then
          deriving a contradiction.
          \begin{smathpar}
          \begin{array}{lr}
            C'(H'(b_1)) = C'(H'(b_2)) & H1\\
          \end{array}
          \end{smathpar}
          Since $b_1 = b$, and $b_2 = b'$, and $C'(H'(b')) = C(H(b'))$:
          \begin{smathpar}
          \begin{array}{lr}
            C'(H'(b)) = C(H(b')) & \\
          \end{array}
          \end{smathpar}
          Since $C'(H'(b')) = C(H(b)) \cup C(H(b'))$:
          \begin{smathpar}
          \begin{array}{lr}
            C(H(b)) \cup C(H(b'))= C(H(b')) & H2\\
          \end{array}
          \end{smathpar}
          From Cor.~3.6 on $\Delta$, we
          know the following:
          \begin{smathpar}
          \begin{array}{lr}
            C(H(b)) - C(L(b,b'))\\
            \hspace*{0.5in}~\cap~ C(H(b')) - C(L(b,b')) ~=~
            \emptyset & H3\\
          \end{array}
          \end{smathpar}
          Rewriting H3 using H2:
          \begin{smathpar}
          \begin{array}{lr}
            C(H(b)) - C(L(b,b'))\\
            \hspace*{0.25in}\cap~~ (C(H(b)) \cup C(H(b')) - C(L(b,b')) ~=~
            \emptyset & \\
          \end{array}
          \end{smathpar}
          Rewriting using Algebraic Law3:
          \begin{smathpar}
          \begin{array}{lr}
            C(H(b)) - C(L(b,b')) ~~\cap\\
            (C(H(b)) - C(L(b,b')) ~\cup~ C(H(b')) - C(L(b,b'))) ~=~ \emptyset & \\
          \end{array}
          \end{smathpar}
          Rewriting using Algebraic Law4:
          \begin{smathpar}
          \begin{array}{lr}
            (C(H(b)) - C(L(b,b')) ~\cap~ C(H(b)) - C(L(b,b')))\\
            ~~\cup~~ (C(H(b)) - C(L(b,b')) ~\cap~ C(H(b')) - C(L(b,b'))) 
            ~=~ \emptyset & \\
          \end{array}
          \end{smathpar}
          Simplifying, and Rewriting using $H3$:
          \begin{smathpar}
          \begin{array}{lr}
            C(H(b)) - C(L(b,b')) ~=~ \emptyset & \\
          \end{array}
          \end{smathpar}
          Which is possible if and only if:
          \begin{smathpar}
          \begin{array}{lr}
            C(H(b)) \subseteq C(L(b,b')) & H4\\
          \end{array}
          \end{smathpar}
          $H0$ and $H4$ now result in a contradiction.

        \item Case $b_2 = b'' \neq b'$: Premises of {\sc Merge}:
          \begin{smathpar}
          \begin{array}{lr}
            C(H(b)) \supset C(L(b,b'))& H1\\
            C(H(b')) \supset C(L(b,b'))& H2\\
            L(b,b'') \reaches L(b',b'') \disj L(b',b'') \reaches
            L(b,b'') & H3\\
          \end{array}
          \end{smathpar}
          From the conclusion of {\sc Merge}:
          \begin{smathpar}
          \begin{array}{lr}
            C'(H'(b)) = C(H(b)) \cup C(H(b')) & H4\\
            C'(H'(b'')) = C(H(b'')) & H5\\
          \end{array}
          \end{smathpar}
          And the premise of the theorem:
          \begin{smathpar}
          \begin{array}{lr}
            C'(H'(b)) = C'(H'(b'')) & \\
          \end{array}
          \end{smathpar}
          Due to $H5$, this is equivalent to:
          \begin{smathpar}
          \begin{array}{lr}
            C'(H'(b)) = C(H(b'')) & H6\\
          \end{array}
          \end{smathpar}
          From Cor.~3.6 on $H'(b')$ and
          $H'(b'') = H(b'')$:
          \begin{smathpar}
          \begin{array}{lr}
            C'(H'(b)) - C'(L'(b,b'')) ~\cap\\
            \hspace*{0.5in}C(H(b'')) - C'(L'(b,b''))
            ~=~ \emptyset & \\
          \end{array}
          \end{smathpar}
          Rewriting using $H6$:
          \begin{smathpar}
          \begin{array}{lr}
            C'(H'(b)) - C'(L'(b,b'')) ~=~ \emptyset & \\
          \end{array}
          \end{smathpar}
          Hence:
          \begin{smathpar}
          \begin{array}{lr}
            C'(H'(b)) \subseteq C'(L'(b,b''))
          \end{array}
          \end{smathpar}
          Rewriting using $H4$:
          \begin{smathpar}
          \begin{array}{lr}
            C(H(b)) \cup C(H(b')) ~\subseteq~ C'(L'(b,b'')) & H7\\
          \end{array}
          \end{smathpar}
          Let us distruct $H3$ and consider the two disjuncts
          separately:
          \begin{itemize}
            \item Case $L(b,b'') \reaches L(b',b'')$: From the
              conclusion of {\sc Merge}:
              \begin{smathpar}
              \begin{array}{lr}
                L'(b,b'') = L(b',b'') & H8\\
              \end{array}
              \end{smathpar}
              Rewriting $H7$ using $H8$:
              \begin{smathpar}
              \begin{array}{lr}
                C(H(b)) \cup C(H(b')) ~\subseteq~ C(L(b',b'')) & H7\\
              \end{array}
              \end{smathpar}
              Which tells us:
              \begin{smathpar}
              \begin{array}{lr}
                C(H(b)) \subseteq C(L(b',b'')) & H9 \\
              \end{array}
              \end{smathpar}
              Note that $L(b',b'')$ is LCA of $H(b')$ and $H(b'')$,
              hence $L(b',b'') \reaches H(b')$. From
              Lemma~3.5, we get:
              \begin{smathpar}
              \begin{array}{lr}
                C(L(b',b'')) \subseteq C(H(b')) & H10\\
              \end{array}
              \end{smathpar}
              From $H9$ and $H10$:
              \begin{smathpar}
              \begin{array}{lr}
                C(H(b)) \subseteq C(H(b')) &  H11\\
              \end{array}
              \end{smathpar}
              Cor.~3.6 on $H(b)$ and
              $H(b')$ tells us:
              \begin{smathpar}
              \begin{array}{lr}
                C(H(b)) - C(L(b,b')) ~\cap\\
                \hspace*{0.5in}C(H(b')) - C(L(b,b')) ~=~
                \emptyset & H12\\
              \end{array}
              \end{smathpar}
              Applying Algebraic Law 5 on $H11$ and $H12$:
              \begin{smathpar}
              \begin{array}{lr}
                C(H(b)) \subseteq C(L(b,b'))
              \end{array}
              \end{smathpar}
              Which contradicts $H1$. Hence $C'(H'(b))$ cannot be
              equal to $C'(H'(b''))$.
